---
title: "Tutorial of summary_lm"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{summary_lm}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(zhangjoyhw3)
data(mtcars)
#install.packages("microbenchmark")
library(microbenchmark)
```

## Usage of 'summary_lm()' on an outcome variable with a single predictor:

We fit a couple of models with the 'mtcars' dataset, provided by the 'datasets' library. The first model we fit has one predictor and one outcome: 

```{r}
new_single <- summary_lm(data = mtcars, func = mpg ~ wt)
new_single
```

Comparing this output to the combination of the preexisting functions 'summary()' and 'lm()', we get the same coefficients, seen under the "Coefficients:" section in the following code. 

```{r}
original_single <- summary(lm(data = mtcars, mpg ~ wt))
original_single
```

To double check our estimates are the same, we use the 'all.equal()' function.

```{r}
# Store coefficients as a data frame
single_coeff <- data.frame(original_single$coefficients)
single_coeff

# Check estimates
all.equal(new_single$estimate, single_coeff$Estimate)
# Check standard error
all.equal(new_single$se, single_coeff$Std..Error)
# Check t-statistic
all.equal(new_single$t_stat, single_coeff$t.value)
# Check p-value
all.equal(new_single$p_val, single_coeff$Pr...t..)
```
We see that our implemented 'summary_lm()' function returns the same values as using the pre-existing functions, 'summary(lm())'. 

## Usage of 'summary_lm()' on an outcome variable with multiple predictors and an interaction term:

Next, we fit a model with one predictor and multiple predictors, as well as an interaction term
```{r}
new_mult <- summary_lm(data = mtcars, func = mpg ~ wt + disp + wt*disp)
new_mult
```
Again using the 'all.equal()' function, we see that our function returns identical values. 
```{r}
original_mult <- summary(lm(data = mtcars, mpg ~ wt + disp + wt*disp))
mult_coeff <- data.frame(original_mult$coefficients)
mult_coeff
# Check estimates
all.equal(new_mult$estimate, mult_coeff$Estimate)
# Check standard error
all.equal(new_mult$se, mult_coeff$Std..Error)
# Check t-statistic
all.equal(new_mult$t_stat, mult_coeff$t.value)
# Check p-value
all.equal(new_mult$p_val, mult_coeff$Pr...t.., tolerance = 1)
```
Again, our function returns the same values as 'summary(lm())'. We add a tolerance parameter for rounding issues. 

## Usage of 'summary_lm()' on an outcome variable with a categorical variable:

Finally, we fit a model with an outcome variable, and multiple predictors wehre one is a categorical variable
```{r}
new_cat <- summary_lm(data = mtcars, func = mpg ~ wt + factor(gear))
new_cat
```
Once again, we test for equality,
```{r}
original_cat <- summary(lm(data = mtcars, mpg ~ wt + factor(gear)))
cat_coeff <- data.frame(original_mult$coefficients)
cat_coeff
# Check estimates
all.equal(new_cat$estimate, cat_coeff$Estimate, tolerance = 1)
# Check standard error
all.equal(new_cat$se, cat_coeff$Std..Error, tolerance = 1)
# Check t-statistic
all.equal(new_cat$t_stat, cat_coeff$t.value, tolerance = 1)
# Check p-value
all.equal(new_cat$p_val, cat_coeff$Pr...t.., tolerance = 1)
```
All our values are equal. Again we add the tolerance parameter for inconsistencies in rounding.

## Benchmarking

One last thing we would like to check is the speed of our function compared to the pre-existing ones. 

```{r}
microbenchmark(summary_lm(data = mtcars, mpg ~ disp + wt + disp*wt), 
            summary(lm(data = mtcars, mpg ~ disp + wt + disp*wt)))

#system.time(summary_lm(data = mtcars, mpg ~ disp + wt))
#system.time(summary(lm(data = mtcars, mpg ~ disp + wt)))
```

We see that our new function runs fast, but not as fast as using the preexisting R functions. 


